---
title: "A/B Test example"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
# assign student
group <- sample(c("A", "B"), size = 1)
```

### AB Testing Example


### Test

In the setup, `group` is randomly assigned.

```
group <- sample(c("A", "B"), size = 1)
```

An internal message is printed listing the message with `context="server-start"`.

```{r context="server-start"}
  # log which group student is assigned to
  message("student assigned: ", group)
```

This is a duplicate, but without server-start.

```{r}
message("student assigned: ", group)
```


Now we randomize the display of the question depending on the group. One code chunk with the question about the letter "A" gets `include = (group == "A")`, so it _should_ be displayed only when "A" is randomly assigned. Another gets the question "B" if `group == "B"`.

```{r letter-a, include = (group == "A")}
question("What number is the letter A?",
  answer("1", correct = TRUE),
  answer("23")
)
```


```{r letter-b, include = (group == "B")}
question("What number is the letter B?",
  answer("2", correct = TRUE),
  answer("23")
)
```
